The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-26 paper/ms.tex
asteroseismic analysis

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue which is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We adopt the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of  either the first~4 or~8 CBVs to each light curve. We note that this can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, but otherwise use the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we will use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} implementation \citep{k2sc}. \textcolor{red}{This is primitive - how do we justify this? We only did it because we didn't have anything cleverer, but now we do. Should I redo this?}.

@@

\textcolor{red}{Guy - can you describe your pipeline in more detail here?}

@@

We obtain good estimates of these asteroseismic parameters for \textcolor{red}{35} targets. In the remainder of cases, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars. \textcolor{red}{Should we try with these?}

@@

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element. We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments at higher resolution and SNR. From this observing run we have 35 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.

We initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values. The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}. Individual elemental abundances are extracted both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these absolute abundance calculations are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.

>>>>

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue which is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We adopt the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of  either the first~4 or~8 CBVs to each light curve. We note that this can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, but otherwise use the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we will use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} implementation \citep{k2sc}. This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy nevertheless for white noise and leads to satisfactory results upon visual inspection of the present sample.

@@

@@

We obtain good estimates of these asteroseismic parameters for 35 targets, presented in Table~\ref{astero_table}. In many of the remainder of cases, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars.

@@

For eight stars, we find that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu. One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model. The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ and used it to calibrate the convective overshoot parameter for low-luminosity red giants. The bulk asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.

\input{astero_table.tex}

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element. We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments at higher resolution and SNR. From this observing run we have~35 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. These are unfortunately not the same~35 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~315, BD+48~290, HD~176209, HD~183354, HD~189636, or HD~189750.

To derive stellar parameters from our TRES spectra, we initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values. The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}. Individual elemental abundances are extracted both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these absolute abundance calculations are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.
